\section{INTRODUCTION}
\subsection{Purpose}
The Software Design Document is a document whose purpose is to provide documentation which will be used to guide the software development, providing all the detailed information for how the software should be built.\\
This document consists of  narrative and graphical documentation of the software design for the project including UML diagrams, object behaviour models, architecture description.
\subsection{Scope}
The Software design document would demonstrate how the design will accomplish the functional and non-functional requirements captured in the RASD for the PowerEnJoy service.
The document describes the high level components and architecture, sub systems, interfaces, database design and algorithm design. This is achieved through the use of architectural patterns, design patterns, and user interfaces. 
\subsection{Definitions, Acronyms, Abbreviations}
\begin{itemize}
	\item \textbf{RASD:} Requirement Analysis and Specification Document
	\item \textbf{ECU:} Electronic Control Unit. 
	\item \textbf{REST:} REpresentational state transfer, is a way of providing interoperability between computer systems on the Internet.
	\item \textbf{CRUD:} Create, Read, Update and Delete.
	\item \textbf{JSON:} JavaScript Object Notation, is serialization of a JavaScript data object.
	\item \textbf{JSP:} JavaServer Pages, a presentation technology for web pages
	\item \textbf{JEE:} Java Enterprise Edition, a development platform for the development of enterprise applications

\end{itemize}
\subsection{Reference Documents}
\begin{itemize}
	\item Project Assignment Document: Assignments AA 2016-2017.pdf 
	\item Requirement Analysis Specification Document: RASD.pdf 
\end{itemize}

\subsection{Document Structure }
In the first part of the document there is a detailed description of the architecture designed for PowerEnjoy service from the logical and physical prospect. All the subsection are a different point of view of the system.
In the second part of the document the focus is on the explanation of some of the algorithms used on the service. In the last section there is a Requirements Traceability that link this document to all the RASD requirements.


\newpage