\section{INTEGRATION STRATEGY}
\subsection{Entry Criteria} 
Before the integration testing can begin, both the RASD and the DD must be completed. Furthermore at least the 80\% of the lines of the code of all components must have been tested with a Unit Test. We strongly suggest the Junit testing framework for Unit Testing.
\subsection{Elements to be Integrated} Identify the components to be integrated, refer to the design document to identify such components in a way that is consistent with your design
\newline 

As we have described in the DD, the main components of the system are:
\begin{itemize}
\item Web Client GUI
\item Mobile Client GUI
\item Driver Client GUI
\item Service Manager 
\item HTTP Server
\item Request Handler
\item REST Parser
\item DBMS
\end{itemize}

In turn, the Service Manager is composed of:
\begin{itemize}
\item Car Manager
\item Trip Manager
\item User Manager
\item Position Manager
\item Fee Manager
\end{itemize}
\noindent
For a further description of the components refer to the Design Document. 
\newline 
Of course, because before the Service Manager can be integrated with other components, the components that compose it have to be integrated.


\subsection{Integration Testing Strategy} 

We have chosen for the Integration Testing a \textbf{bottom up} approach. This means that the integration will regard first the low-level components. For this type of testing, because we start from the low level components, we will need some \textbf{drivers}. These are temporary modules that simulate the behaviour of the higher level components and do the calls of the functions of lower level components. \newline
That reason why we have chosen the bottom-up approach are:

\begin{itemize}
\item The lowest level component of our system is the DBMS, impletemented with MySQL 5.6. MySQL is a well-known software component that is available on the market. So the DBMS is ready to use and is a robust starting point for the Integration Testing. Starting from this we can begin to integrate the component of Backend of our system, that essentialy is the Service Manager component. 
\item The low level components that compose the Backend of our service are the biggest part of our system and all the other components depends on them. Because of this importance of the low level components, the best choice is to start from them and, when it's sure that they work well together, integrate the other components.
\end{itemize}  


\subsection{Sequence of Component/Function Integration} 
\subsubsection{Software Integration Sequence} For each subsystem, identify the sequence in which the software components will be integrated within the subsystem; relate this sequence to any product features that are being built up
\subsubsection{Subsystem Integration Sequence} Identify the order in which subsystems will be integrated;  if you have a single subsystem, 2.4.1 and 2.4.2 have to be merged in a single section





