\section{Scenarios}

\subsection{Scenario 1}

Andrew is a student. Because in his home city there aren't the courses he wants to attend, he moves to another city. There he rents a flat with other students. During the week he doesn't need any mean of transport and travels only on foot,  because his house is very near to the university. In the weekend Andrew wants to have some fun with his friends, but	unfortunately the areas with the coolest bars are far from his house and at night there aren't public transports going to those area. Furthermore neither he or his friends have a car, because they are all out of their home towns. So Andrew uses his Power EnJoy application, searches a car near his address, reserves a car, reaches it and drives till his favorite fun area, carrying with him some of his friends.

\subsection{Scenario 2}

It's Friday night and Bob have to go out with his girlfriend. Unfortunately his parents are away and have the car with them, so Bob searches a car near his home using Power EnJoy application. He sees on the map that there is only one car near his house and that its autonomy allows him only to reach his girlfriend's house. He looks for a special parking area near his girlfriend's house and finds one.
So he decides to go to that special parking area, leave there the car, plug it into the power grid and request again for that car. Then he waits there for his girlfriends, having enough charge when she arrives to go downtown.

\subsection{Scenario 3}

Jim and Kate are two young tourists. They walked a lot all the day and so now they want to find an easy way to go to their hotel.
Jim his registered to the Power EnJoy car-sharing service, so his reserves and picks up a car. They decide to park the car near the hotel, but when they're going to do that, they see a message telling that they are more than 3 km far from the nearest power station. Because Jim knows would have to pay more because of that and he hasn't a lot of money left, he decides to park nearer to a power station.
    
\subsection{Scenario 4}

Lucas need to go to do some shopping downtown on Sunday morning but on that date the municipal administration set a cars ban.
He walk using Power EnJoy application on his mobile phone to reach the nearest Special parking areas where he has reserved an electric car that allow him to go downtown even with the ban.
