\todo[inline]{List of issue and issue latex command}


\subsection{Naming Conventions}
\begin{itemize}
\item[1] No issue
\item[2] No issue - No one-character variable is used
\item[3] No issue
\item[4] No issue - There isn't any interface
\item[5] Issue at line 46 - The first letter of the method "DoGet(HttpServletRequest request, HttpServletResponse response)" is capitalized
\item[6] No issue
\item[7] No issue - There isn't any constant
\end{itemize}
\subsection{Indention}
\begin{itemize}
\item[8] No issue - Always three spaces are used for indention
\item[9] No issue - No tabs found in the code
\end{itemize}
\subsection{Braces}
\begin{itemize}
\item[10] No issue - Kernighan and Ritchie style is used consistently.
\item[11] No issue - There are only \textit{if} statements and they are all surrounded by curly braces.
\end{itemize}

\subsection{File Organization}
\begin{itemize}
\item[12] No issue - All sections are separated by a blank line.
\item[13] \begin{itemize}
\item Issue at line 35 - Length = 82 - It is impractical to split the last word.
\item Issue at line 40 - Length = 82 - It is impratical to split the method "getName()"
\item Issue at line 43 - Length = 128 - "javax.servlet.http.HttpServletResponse)" could be put in the following line
\item Issue at line 46 - Length = 119 - impractical to put the \textit{throw} declaration in the following line
\item Issue at line 55 - Length = 119 - impractical to put the \textit{throw} declaration in the following line
\item Issue at line 57 - Length = 83 - impractical to split the method.
\item Issue at line 70 - Length = 87 - impractical to split the method
\item Issue at line 74 - Length = 87 - impractical to split the method
\end{itemize}
\item[14] Issue at line 43 - Length = 128 - See [13]
\end{itemize}
\subsection{Wrapping Lines}
\begin{itemize}
\item[15] No issue - No line breaks
\item[16] No issue - No line breaks
\item[17] No issue - Expressions are all aligned.
\end{itemize}
\subsection{Comments}
\begin{itemize}
\item[18] Comments are used only for briefly explain what the class does and to give a reference to the method that the "doGet" method overrides. There are no comments for the "forwardUrl" method and for blocks of code.
\item[19] No issue - There is no commented out code 
\end{itemize}
\subsection{Java Source Files}
\begin{itemize}
\item[20] No issue
\item[21] No issue
\item[22] No issue
\item[23] No issue
\end{itemize}
\subsection{Package and Import Statements}
\begin{itemize}
	\item[24] \textbf{Lines 31:}\code{ import org.apache.ofbiz.security.Security;	}\\
	\textbf{Unused import.}\\
	\textbf{Solution: } Remove the unused import line.
	
\end{itemize}
\subsection{Class and Interface Declarations}
\begin{itemize}
\item[25]
\begin{itemize}
\item[a] No issue
\item[b] No issue
\item[c] No issue - No implementation comments
\item[d] No issue
\item[e] No issue - No instance variables
\item[f] No issue - No constructors
\item[g] No issue
\end{itemize}
\item[26] No issue - There are only two methods
\item[27]
\begin{itemize}
\item No duplicates
\item Methods aren't too long (24 lines for forwardUrl and 7 lines for doGet)
\item The class isn't too big (45 lines)
\item No breaking encapsulation - The only attribute (module) is final.
\item The cohesion is high, because all the methods work to implement the main functionality of the server, that is get and forward information.
\item Coupling is low, because the methods are independent.
\end{itemize}
\end{itemize}

\subsection{Initialization and Declarations}
\begin{itemize}
\item[28] No issue
\item[29] No issue
\item[30] No issue 
\item[31] No issue
\item[32] No issue
\item[33] No issue
\end{itemize}
\subsection{Method Calls}
\begin{itemize}
\item[34] No issue
\item[35] No issue
\item[36] No issue 
\end{itemize}

\subsection{Arrays}
\begin{itemize}
	\item No arrays are used in the class behavior.
\end{itemize}
\subsection{Object Comparison}
\begin{itemize}
\item[40] There isn't any comparison
\end{itemize}
\subsection{Output Format}
There is no displayed output.
\subsection{Computation, Comparisons and Assignments}
\begin{itemize}
\item[44] No issue - All the operations seem to be effective and concise and there is no evidence of the use of brute force solutions
\item[45-46] No issue - The only operations present in the code are the AND operations at lines 70 and 74 and they involve only one operation between two elements, so they don't need the management of precedences.
\item[47] No issue - There isn't any division
\item[48] No issue - There isn't any arithmetic expression
\item[49] No issue- There isn't any comparison
\item[50] No issue - There isn't any throw-catch expression
\item[51] No issue - There is only one type conversion and is explicit (line 57):
\begin{lstlisting}[language=java]
GenericValue userLogin = (GenericValue) session.getAttribute("userLogin");
\end{lstlisting}
\end{itemize}
\subsection{Exceptions}
\begin{itemize}
\item[52] No issue - The two methods throw appropriate exceptions, declared in their header
\item[53] No issue - There isn't any throw-catch statement. The exception handled are declared in the headers and they are well-known and reliable java exceptions 
\end{itemize}
\subsection{Flow of Control}
No \code{switch} statement are used in the class.\\
No loop statements are used in the class.
\subsection{Files}
No files are used in the class.